---
title: "Using GRanger object in goslingr"
output: rmarkdown::html_vignette
vignette: >
%\VignetteIndexEntry{Using GRanger object in goslingr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
  ```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup, message=FALSE, results="hide"}
library(goslingr)
library(GenomicRanges)
```
## Getting a sample data for the GRanges object

We will be loading the peaks data from ChipSeq dataset with the GEO accession [GSM1295076](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM1295076)

`GSM1295076_CBX6_BF_ChipSeq_mergedReps_peaks.bed.gz` file will be used to create a sample GRanges object.

```{r, reading-data}
url <- "https://rb.gy/7y3fx"
temp_file <- file.path(tempdir(), "data.gz")
download.file(url, destfile = temp_file, method = "auto", mode = "wb")
df <- read.delim(
  temp_file,
  header = FALSE,
  comment.char = "#",
  sep = ""
)
gr <- GRanges(
  seqnames = df$V1,
  ranges = IRanges(df$V2, df$V3, peak = df$V5)
)
gr
```
## Creating our gosling spec

Now that we have a GRanges object, we can generate our spec:
```{r}

spec <- list(
  title = "Basic Marks: bar",
  subtitle = "Tutorial Examples",
  tracks = list(
    create_track(
      layout = "linear",
      width = 800,
      height = 180,
      mark = "bar",
      x = list(field = "start", type = "genomic", axis = "bottom"),
      xe = list(field = "end", type = "genomic"),
      y = list(field = "peak", type = "quantitative", axis = "right"),
      size = list(value = 5),
      data = create_gr_data(gr)
    )
  )
)

goslingr(spec)
```
